The effects of varying depth in cosmic shear surveys

### 2019-10-11 paperdraft.tex
added the second batch of catherine's suggestion

\begin{figure*}
\begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{images/mcmc_kids.pdf}
\end{subfigure}
\begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{images/mcmc_euclid.pdf}
\end{subfigure}
\caption{Results of the MCMC simultation to estimate the bias caused by a variation of depth in a cosmic shear survey for a KiDS450-like (left) and KiDS$15\,000$-like survey (right). The left simulation was computed using the covariance matrix of H18. As Euclid will cover approx. $15\,000\,\rm{deg}^2$, the covariance matrix of the KiDS$15\,000$-like survey is the one of H18 divided by 30. Note that this does not include the higher number density and better shape measurements of Euclid, so that thi Both simulations were computed using a fiducial cosmology of $\Omega_{\rm{m}}=0.25$ and $\sigma_8 = 0.85$.}
\label{fig:mcmc_results}
\end{figure*}

>>>>

\begin{figure*}
\begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{images/mcmc_kids.pdf}
\end{subfigure}
\begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{images/mcmc_euclid.pdf}
\end{subfigure}
\caption{Results of the MCMC simultation to estimate the bias caused by a variation of depth in a cosmic shear survey for a KiDS450-like (left) and KiDS$15\,000$-like survey (right). The left simulation was computed using the covariance matrix of H18. As Euclid will cover approx. $15\,000\,\rm{deg}^2$, the covariance matrix of the KiDS$15\,000$-like survey is the one of H18 divided by 30. Note that this does not include the higher number density and better shape measurements of Euclid, so that this figure constitutes an extremely conservative estimate on this effect for Euclid. Both simulations were computed using a fiducial cosmology of $\Omega_{\rm{m}}=0.25$ and $\sigma_8 = 0.85$.}
\label{fig:mcmc_results}
\end{figure*}
